\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, enumitem, multicol}

\everymath{\displaystyle}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{definition*}{Definition}
\newcommand{\vct}[1]{\langle #1 \rangle}
\newcommand{\vu}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\vw}{\mathbf{w}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vn}{\mathbf{n}}

\newcommand{\colvecTwo}[2]{
  \begin{bmatrix}
    #1 \\
    #2
  \end{bmatrix}
}
\newcommand{\colvecThree}[3]{
  \begin{bmatrix}
    #1 \\
    #2 \\
    #3
  \end{bmatrix}
}

\newcommand{\casesTwo}[2]{
  \begin{cases}
    #1 \\
    #2
  \end{cases}
}
\newcommand{\casesThree}[3]{
  \begin{cases}
    #1 \\
    #2 \\
    #3
  \end{cases}
}

\title{Linear Algebra: A Modern Introduction}
\author{David Poole}
\date{}

\begin{document}
\maketitle
\setcounter{section}{1}
\section{Systems of Linear Equations}

\subsection{Introduction to Systems of Linear Equations}
\begin{definition*}
  A linear equation in the $n$ variables $x_1, x_2, \ldots, x_n$ is an equation that can be writen
  in the form
  \[a_1x_1+a_2x_2+\cdots+a_nx_n=b\]
  where the coefficients $a_1, a_2, \ldots, a_n$ and the constant term $b$ are constants.
\end{definition*}
\subsubsection*{Exercises}
\begin{enumerate}
    \begin{multicols}{3}
    \item Yes
    \item No
    \item No
    \item No
    \item No
    \item Yes
    \end{multicols}
  \item $2x+4y=7$
  \item $x+y=1, x \ne y$
  \item $x+y=4, x\ne0, y\ne0$
  \item $x-100y=0, x>0, y>0$
    \setcounter{enumi}{38}
  \item
    \begin{enumerate}
      \item $2x+y=3$
      \item $x=\frac{3}{2}-\frac{1}{2}s, y=s$
    \end{enumerate}
    \setcounter{enumi}{40}
  \item
    \begin{align*}
      2t+3s & = 0 \\
      3t+4s & = 1
    \end{align*}
    $x=\frac{1}{3},y=2\frac{1}{2}$
\end{enumerate}

\subsection{Direct Methods for Solving Linear Systems}
\begin{definition*}
  A matrix is in \textbf{row echelon form} if it satisfies the following properties:
  \begin{enumerate}
    \item Any rows consisting entirely of zeroes are at the bottom.
    \item In each nonzero row, the first nonzero entry (called the \textbf{leading entry}) is in a
      column to the left of any leading entries below it.
  \end{enumerate}
\end{definition*}
\begin{definition*}
  The following \textbf{elementary row operations} can be performed on a matrix:
  \begin{enumerate}
    \item Interchange two rows.
    \item Multiply a row by a nonzero constant.
    \item Add a multiple of a row to another row.
  \end{enumerate}
\end{definition*}
\begin{definition*}
  Matrices $A$ and $B$ are \textbf{row equivalent} if there is a sequence of elementary row
  operations that converts $A$ into $B$.
\end{definition*}
\begin{theorem*}
  Matrices $A$ and $B$ are row equivalent if and only if they can be reduced to the same row echolon
  form.
\end{theorem*}
\begin{proof}
  If $A$ and $B$ are row equivalent, the further row operations will reduce $B$ (which $A$ can be
  converted to) to some (same) row echelon form.

  Conversely, if $A$ and $B$ have the same row echelon form $R$, then, via elementary row
  operations, we can convert $A$ into $R$ and $B$ into $R$. Reversing the latter sequence of
  operations, we can convert $R$ into $B$, and therefore the sequence $A\to R\to B$ achieves the
  desired effect.
\end{proof}
\begin{definition*}
  The \textbf{rank} of a matrix is the number of nonzero rows in its row echelon form.
\end{definition*}
\begin{theorem*}[The Rank Theorem]
  Let $A$ be the coefficient matrix of a system of linear equations with $n$ variables. If the
  system is consistent, then
  \[\text{numer of free variables}=n-\operatorname{rank}(A).\]
\end{theorem*}
\begin{definition*}
  A system of linear equations is called \textbf{homogeneous} if the constant term in each equation
  is zero.
\end{definition*}
\subsubsection*{Exercises}
\begin{enumerate}
  \item No
  \item Yes; No
  \item Yes; Yes
  \item Yes; Yes
  \item No
  \item No
  \item Yes; No
  \item Yes; No
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          1 & 1 & 1 \\
          0 & 1 & 1 \\
          0 & 0 & 1
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 0 & 0 \\
          0 & 1 & 0 \\
          0 & 0 & 1
        \end{bmatrix}
        $
    \end{enumerate}
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          4 & 3 \\
          0 & -\frac{1}{2}
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 0 \\
          0 & 1
        \end{bmatrix}
        $
    \end{enumerate}
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          3 & 5 \\
          0 & -\frac{31}{3} \\
          0 & 0
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 0 \\
          0 & 1 \\
          0 & 0
        \end{bmatrix}
        $
    \end{enumerate}
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          2 & -4 & -2 & 6 \\
          0 & 7 & 9 & -3
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 0 & \frac{11}{7} & \frac{15}{7} \\
          0 & 1 & \frac{9}{7} & -\frac{3}{7}
        \end{bmatrix}
        $
    \end{enumerate}
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          3 & -2 & -1 \\
          0 & \frac{1}{3} & -\frac{1}{3} \\
          0 & 0 & 0
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 0 & -1 \\
          0 & 1 & -1 \\
          0 & 0 & 0
        \end{bmatrix}
        $
    \end{enumerate}
  \item
    \begin{enumerate}
      \item
        $
        \begin{bmatrix}
          -2 & -4 & 7 \\
          0 & 0 & -\frac{1}{2} \\
          0 & 0 & \frac{1}{2}
        \end{bmatrix}
        $
      \item
        $
        \begin{bmatrix}
          1 & 2 & 0 \\
          0 & 0 & 1 \\
          0 & 0 & 0
        \end{bmatrix}
        $
    \end{enumerate}
    \setcounter{enumi}{18}
  \item The first step cannot be done at the same time.
  \item Swapping $R_1$ and $R_2$.
  \item $3R_2\to R_2+(-2)R1$.
    \setcounter{enumi}{22}
  \item 3, 2, 2, 0, 2, 3, 4, 3
  \item 8 forms.
  \item $\colvecThree{x}{y}{z}=\colvecThree{2}{5}{1}$
  \item No solution.
  \item $\colvecThree{x}{y}{z}=t\colvecThree{5}{1}{1}$
  \item $\colvecTwo{s}{t}=\colvecTwo{2}{-1}$
    \setcounter{enumi}{34}
  \item Unique solution.
  \item No solution.
  \item Infinitely many solutions.
    \setcounter{enumi}{39}
  \item
    \begin{enumerate}
      \item No values.
      \item $k\ne-1$
      \item $k=-1$
    \end{enumerate}
    \setcounter{enumi}{44}
  \item $\colvecThree{x}{y}{z}=\colvecThree{\frac{27}{21}}{-\frac{17}{7}}{0}
    +t\colvecThree{\frac{13}{7}}{-\frac{10}{7}}{1}$
    \setcounter{enumi}{47}
  \item $\colvecThree{0}{4}{0}$
  \item Not intersect.
  \item $a, b, c$ should satisfy $a-2b-c+6=0$.
    \setcounter{enumi}{52}
  \item $\colvecTwo{x}{y}=\colvecTwo{0}{2}$
  \item $\colvecThree{x}{y}{z}=\colvecThree{0}{1}{1}$
    \setcounter{enumi}{58}
\end{enumerate}

\subsection{Spanning Sets and Linear Independence}
\begin{theorem*}
  A system of linear equations with augmented matrix $[A|\mathbf{b}]$ is consistent if and only if
  $\mathbf{b}$ is a linear combination of the columns of $A$.
\end{theorem*}
\begin{definition*}
  If $S=\{\mathbf{v_1}, \mathbf{v_2}, \ldots, \mathbf{v_k}\}$ is a set of vectors in $\mathbb{R}^n$,
  then the set of all linear combinations of $\mathbf{v_1}, \mathbf{v_2}, \ldots, \mathbf{v_k}$ is
  called the \textbf{span} of $\mathbf{v_1}, \mathbf{v_2}, \ldots, \mathbf{v_k}$ and is denoted by
  $\operatorname{span}(\mathbf{v_1}, \mathbf{v_2}, \ldots, \mathbf{v_k})$ or
  $\operatorname{span}(S)$. If $\operatorname{span}(S)=\mathbb{R}^n$, then $S$ is called a
  \textbf{spanning set} for $\mathbb{R}^n$.
\end{definition*}
\begin{theorem*}
  Vectors $\mathbf{v_1}, \mathbf{v_2}, \ldots, \mathbf{v_k}$ in $\mathbb{R}^n$ are linearly
  independent if and only if at least one of the vectors can be expressed as a linear combination of
  the others.
\end{theorem*}
\subsubsection*{Exercises}
\begin{enumerate}
  \item Yes
  \item No
  \item No
  \item Yes
  \item No
  \item Yes
  \item Yes
  \item Yes
  \item Any vectors $\colvecTwo{a}{b}$ can be written as $\frac{a+b}{2}\colvecTwo{1}{1}+
    \frac{a-b}{2}\colvecTwo{1}{-1}$.
    \setcounter{enumi}{12}
  \item
    \begin{enumerate}
      \item Line $t\colvecTwo{2}{-4}$.
      \item $2x+y=0$.
    \end{enumerate}
    \setcounter{enumi}{14}
  \item
    \begin{enumerate}
      \item Plane $\vx=\mathbf{s}\colvecThree{1}{2}{0}+\mathbf{t}\colvecThree{3}{2}{-1}$.
      \item $2x-y+4z=0$.
    \end{enumerate}
    \setcounter{enumi}{16}
  \item $a=-3c, b=0$.
    \setcounter{enumi}{18}
  \item
    \begin{align*}
      \vu & = \vu+0(\vu+\vv)+0(\vu+\vv+\vw) \\
      \vv & = -\vu+(\vu+\vv)+0(\vu+\vv+\vw) \\
      \vw & = 0\vu-(\vu+\vv)+(\vu+\vv+\vw)
    \end{align*}
    \setcounter{enumi}{21}
  \item Linearly independent.
  \item Linearly independent.
    \setcounter{enumi}{24}
  \item Linearly dependent
    \setcounter{enumi}{42}
  \item
    \begin{enumerate}
      \item Yes.
      \item No.
    \end{enumerate}
\end{enumerate}

\subsection{Applications}
\subsection{Iterative Methods for Solving Linear Systems}

\end{document}
